Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-19 krs-survey.tex
Moved the section on memory to the end of 3.2 How things are represented
Addded section on OMRKF + minor other changes

\emph{Default logic} is one of the formal logic that account for representing
general truth and exceptions to it. However, due to computational complexity of
these model (most of inferences in default logic are known to be $NP$-complete
problem), classical logics and most of the existing reasoners do not allow
non-monotonic reasoning. For instance, the SWRL rule language, usually
associated to the OWL-DL ontology language, do not allow non-monotonic
reasoning.

@@

\subsubsection{Presupposition accommodation}
\label{sect|presupposition-accomodation}

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{http://ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & & Mavridis, Roy \par (MIT MediaLab) & & & & & \cite{Mavridis2006} \\
OMKRF & & Suh et al. \par (Hanyang Univ.) & & & & & \cite{Suh2007} \\
DY-KNOW & & Heintz, Dowerty \par (Linköping Univ.) & & & & & \cite{Heintz2004} \\
Ke Jia & & Chen et al. \par (Univ. of Science and Technology of China) & & & & & \cite{Chen2010} \\
 & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\
 & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\
ARMAR & & Schmidt-Rohr (Karlsruhe TH) \\
 & & Hertzberg (Osnabrück Univ.) \\
 & & (DFKI Bremen) \\
 (based on {\sc KnowRob} & & (JSK) \\

@@

\subsubsection{Intrinsic features}
\label{sect|peis-intrinsic-features}

\paragraph{Expressiveness} The PEIS Knowledge representation system relies on
the {\sc ResearchCyc} and {\sc CycL} language to represent knowledge. The {\sc CycL} language
allows to represent first order logic sentences and has extensions for modal logics and higher order logics.

@@

\subsubsection{Anchoring strategies}
\label{sect|peis-anchoring}

@@

@@

\subsubsection{Integration in the robot architecture}
\label{sect|peis-integration}

@@

@@

\begin{tabular}{lp{4cm}}
\hiderowcolors
{\bf Project} & {\bf Common-sense \par knowledge source} \\
\hline
\showrowcolors
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
DY-KNOW & \\
OMKRF & \\
GSM &  \\
NKLR &  None \\
CAST Proxies &  None \\
Wrighteagle & \\
Vincze & \\
ARMAR &  \\
Hertzberg (Osnabrück) & \\
(DFKI Bremen) & \\
(JSK) & \\

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{l|ccccccccc}
\hiderowcolors

{} & {\sc KnowRob} & {ORO} & {\sc PEIS} & {\sc CAST} & {\sc Golog} & {\sc NKRL} & {\sc GSM} & {\sc OMKRF} & {\sc DY-KNOW} \\

\hline
\showrowcolors
{\bf Expressiveness} & & & & & & & & &  \\
Formal Logic & Prolog & OWL-DL & {\sc CycL} &  &  &  & & & \\
OWA/CWA & CWA & OWA & & & & & & & \\
Modeling uncertainty & +++ (add-on) & & & & & & & & \\
Meta-cognition & ++ & ++ & & & & & & & \\
{\bf Model} & & & & & & & & &  \\
{\bf Reasoning} & & & & & & & & &  \\
Standard FOL reasoning & +++ & +++ & & & & & & &  \\
Lazy evaluation & +++ & & & & & & & &  \\
Reasoning under uncertainty & ++ (add-on) & & & & & & & & \\
Non-monotonic reasoning & & & & & & & & &  \\
Presupposition accomodation & & & & & & & +++ & &  \\
Prediction, projection, diagnosis & & & & & & & & &  \\
Physics-based reasoning & +++ (add-on) & & & & & & & &  \\
Planning & + & +++ (external module) & & & & & & &  \\
Knowledge structure alteration & & ++ & & & & & & &  \\
Learning & & & & & & & & &  \\
{\bf Knowledge Acquisition} & & & & & & & & &  \\
{\bf Integration} & & & & & & & & &  \\
{\bf Knowledge Instanciation} & & & & & & & & &  \\
\hline

>>>>

\emph{Default logic} is one of the formal logic that account for representing
general truth and exceptions to it (for instance, \emph{tomatoes are red, in
general}). However, due to computational complexity of these model (most of
inferences in default logic are known to be $NP$-complete problem), classical
logics and most of the existing reasoners do not allow non-monotonic reasoning.
For instance, the SWRL rule language, usually associated to the OWL-DL ontology
language, do not allow non-monotonic reasoning.

@@

\subsubsection{Presupposition Accommodation}
\label{sect|presupposition-accomodation}

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{http://ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & & Mavridis, Roy \par (MIT MediaLab) & & & & & \cite{Mavridis2006} \\
OMRKF & & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe/?mid=symbolic_reasoning} & ? & Horn Clauses & ? & \cite{Suh2007} \\
DY-KNOW & & Heintz, Dowerty \par (Linköping Univ.) & & & & & \cite{Heintz2004} \\
Ke Jia & & Chen et al. \par (Univ. of Science and Technology of China) & & & & & \cite{Chen2010} \\
 & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\
 & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\
ARMAR & & Schmidt-Rohr (Karlsruhe TH) \\
 & & Hertzberg (Osnabrück Univ.) \\
 & & (DFKI Bremen) \\
 (based on {\sc KnowRob} & & (JSK) \\

@@

\paragraph{Knowledge model} The PEIS Knowledge representation system relies on
the {\sc ResearchCyc} and {\sc CycL} language to represent knowledge. The {\sc CycL} language
allows to represent first order logic sentences and has extensions for modal logics and higher order logics.

@@

@@

The system can ask the human for help to disambiguate between concept names.

@@

\paragraph{Integration in the robot architecture}
\label{sect|peis-integration}

@@

\subsection{OMRKF}
\label{sect|omrkf}

The Ontology-based Multi-layered Robot Knowledge Framework~\cite{Suh2007}
(OMKRF) is a knowledge representation system based on four inter-related
\emph{classes} of knowledge (Figure~\ref{fig|omrkf}). It proposes a layered
approach to knowledge representation that allows to integrate the grounding
process to the knowledge representation process. OMRKF knowledge model is
implemented with Horn clauses.

\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{omrkf.pdf}

    \caption{OMRKF organizes knowledge into four \emph{classes}, each composed
    of three \emph{levels}. The figure shows some examples of link between
    knowledge classes and knowledge levels. Based on~\ref{Suh2007}.}

    \label{fig|omrkf}
\end{figure}

Each level of knowledge is build as three stages of ontological realization: a
\emph{meta-concept} (the level itself, like ``temporal context'', ``behaviour''
or ``object feature'', a taxonomy of concepts inside this level (for instance
$cup : Object \sqsubseteq tableware : Object$) and an instanciation of the
taxonomy ($cup1 : cup$).

Environment is represented in OMRKF in the $space : Model$ knowledge level as a
classical three layers mapping (metric, topological and semantic maps). Objects
(in $object : Model$) are localized in $space : Model$ through Voronoi nodes.

The knowledge class $Context$ proposes an explicit statement of spatial context
(mostly geometric relations between objects), temporal context and a more
general \emph{high-level} context, inferred from spatial and temporal contexts.

Finally, the $Activity$ knowledge class store coumpound actions in a HTN-like
structure, exploited at run-time by a planner.

\paragraph{Experiments} Experiments conducted with OMRKF include finding
kitchen objects and reporting about their state to a human.  This experiment
also shows how OMRKF can deal with objects only partially matched by their
descriptor by introducing a $candidate()$ function.

@@

\begin{tabular}{lp{4cm}}
\hiderowcolors
{\bf Project} & {\bf Common-sense \par knowledge source} \\
\hline
\showrowcolors
{\sc KnowRob} & {\sc OpenCyc}, processed web content, custom OWL-DL ontology \\
ORO & {\sc OpenCyc}, custom OWL-DL ontology \\
PEIS Ecology & {\sc ResearchCyc} \\
DY-KNOW & \\
OMRKF & {\it A priori} knowledge structure and axioms, custom set of instances\\
GSM &  \\
NKLR &  None \\
CAST Proxies &  None \\
Wrighteagle & \\
Vincze & \\
ARMAR &  \\
Hertzberg (Osnabrück) & \\
(DFKI Bremen) & \\
(JSK) & \\

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{4.5cm}|ccccccccc}
\hiderowcolors

{} & {\sc KnowRob} & {ORO} & {\sc PEIS} & {\sc CAST} & {\sc Golog} & {\sc NKRL} & {\sc GSM} & {\sc OMRKF} & {\sc DY-KNOW} \\

\hline
\showrowcolors
{\bf Expressiveness} & & & & & & & & &  \\
Logical formalism & Prolog & OWL-DL & {\sc CycL} &  &  &  & & Horn clauses & \\
Expressive power & & & & & & & & &  \\
OWA/CWA & CWA & OWA & & & & & & & \\
Modeling uncertainty & +++ (extension) & & & & & & & + (\emph{candidate} entities) & \\
Meta-cognition & ++ & ++ & & & & & & & \\
{\bf Model} & & & & & & & & &  \\
Representation of space & & & & & & & & ++ &  \\
Representation of temporality & & & & & & & & + &  \\
Context & & & & & & & & ++ &  \\
Alternative worlds & & +++ & & & & & & &  \\
Introspection & + (SRDF) & & & & & & & &  \\
Memory & & + & & & & & & &  \\
{\bf Reasoning} & & & & & & & & &  \\
Standard FOL reasoning & +++ & +++ & & & & & & &  \\
Knowledge structure alteration & & ++ & & & & & & &  \\
Lazy evaluation & +++ & & & & & & & &  \\
Reasoning under uncertainty & ++ (extension) & & & & & & & & \\
Non-monotonic reasoning & & & & & & & & &  \\
Presupposition accomodation & & & & & & & +++ & &  \\
Prediction, projection, diagnosis & & & & & & & & &  \\
Physics-based reasoning & +++ (extension) & & & & & & & &  \\
Planning & + & +++ (external module) & & & & & & &  \\
Learning & & & & & & & & &  \\
{\bf Knowledge Acquisition} & & & & & & & & &  \\
Acquisition techniques & & & & & & & & &  \\
Grounding & & & & & & & & &  \\
Instanciation & & & & & & & & &  \\
{\bf Integration} & & & & & & & & &  \\
...with sensori-motor layers & & & & & & & & &  \\
...with executive layers & & & & & & & & &  \\
Monitoring and debugging & & & & & & & & &  \\
Performances & & & & & & & & &  \\
